---
title: "`r paste0('Data-driven species trends in ',aoiFullName)`"
subtitle: "`r paste0(as.data.frame(git2r::repository())[1,2],'. repo https://github.com/Acanthiza/SppTrends/commit/',substr(as.data.frame(git2r::repository())[1,1],1,7))`"
author:
- Department for Environment and Water
date: "`r format(Sys.time(), '%A, %d %B, %Y. %H:%M')`"
output:
  bookdown::word_document2:
    toc: no
    toc_depth: 3
    reference_docx:           common/Styles.docx
    fig_caption: yes
link-citations: no
csl:                          common/BibStyle.csl
bibliography:                 [common/refs.bib,packageRefs.bib,datasetRefs.bib]
---


# Setup code

```{r setup, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}

  library("timeR")
  reportTimer <- createTimer(precision = "ms"
                             , verbose = FALSE
                             )
  
  reportTimer$start("report")

  if(!exists("packages")) source("0005_setup.R")
  
  knitcitations::cleanbib()
  options("citation_format" = "pandoc")

```

# Import

```{r importTaxa}

  if(!exists("taxaAll")) source("0010_import_taxa.R")

```

Records were extracted from the Global Biodiversity Information Facility using the `occ_download` function in the `rgbif` package `r cite_package("rgbif")`.

Total records: `r format(nrow(taxaAll),big.mark = ",")` [`r paste0("@",refsGBIF[1,2])`].


# Tidy

```{r tidy}

  if(!exists("dat")) source("0020_tidy.R")

```

Area of interest: `r aoiFullName`, defined by `r vec_to_sentence(aoiName)` IBRA Subregions.

Total tidied records: `r format(nrow(dat),big.mark=",")`.

```{r analysis}

  if(!exists("taxaModsFull")) source("0030_Analysis.R")

```

```{r include=FALSE}

  taxGroupExp = NULL

  taxGroupNames <- taxaModsFull %>%
    dplyr::distinct(!!ensym(taxGroup)) %>%
    dplyr::mutate(gbifInfo = map(!!ensym(taxGroup),name_backbone)) %>%
    tidyr::unnest(cols = c(gbifInfo)) %>%
    dplyr::mutate(Common = map_chr(usageKey,get_gbif_common))

  taxGroupLoop <- taxaModsFull %>%
    dplyr::pull(!!ensym(taxGroup)) %>%
    unique() %>%
    sort() %>%
    {if(testRmd) sample(.,3) else .} %>%
    gsub(" ","",.)
    

  for (i in taxGroupLoop) {
    
    thisTaxGroup <- i
    
    taxGroupExp = c(taxGroupExp, knit_expand('child/taxGroupExp.Rmd'))
    
  }

```

`r paste(knit(text = taxGroupExp), collapse = '\n')`

# Appendix

## Run times

Table \@ref(tab:runtimes) shows the time taken to run this report, and import, tidy, model and visualise the data presented.

```{r runtimes}

  reportTimer$stop("report", comment = "creation of .docx from .rmd")

  kable(read_feather(path(outDir,"timer.feather")) %>%
          #dplyr::bind_rows(read_feather(path("out","extractTimer.feather"))) %>%
          dplyr::bind_rows(getTimer(reportTimer)) %>%
          dplyr::mutate(timeElapsed = round(timeElapsed,1))
        , caption = "Timing of the various components that make up this report"
        )

```

# References
