```{r data{{thisTaxa}}}

  summariseTaxa <- "{{thisTaxa}}"

  thisTaxaData <- datTidy %>%
    dplyr::mutate(thisTaxa = gsub(" ","",Taxa)) %>%
    dplyr::filter(thisTaxa == summariseTaxa)
  
  thisTaxaCooccur <- sppCooccur %>%
    dplyr::mutate(thisTaxa = gsub(" ","",Taxa)) %>%
    dplyr::filter(thisTaxa == summariseTaxa)

  thisTaxaMods <- taxaMods %>%
    dplyr::mutate(thisTaxa = gsub(" ","",Taxa)) %>%
    dplyr::filter(thisTaxa == summariseTaxa) %>%
    dplyr::mutate(modLoop = paste0(thisTaxa,gsub(" ","",type)))
  
  thisTaxaRed <- red %>%
    dplyr::mutate(thisTaxa = gsub(" ","",Taxa)) %>%
    dplyr::filter(thisTaxa == summariseTaxa)

  taxa <- thisTaxaMods$Taxa[[1]]

  common <- thisTaxaMods$Common[[1]]
  
```

## _`r taxa`_: `r common`

### Summary

_`r taxa`_ had `r format(nrow(thisTaxaData),big.mark = ",")` records in the tidied data set across `r n_distinct(thisTaxaData$geo1) %>% numbers2words()` IBRA Regions (`r unique(thisTaxaData$geo1) %>% vec_to_sentence`) and `r n_distinct(thisTaxaData$geo2) %>% numbers2words()` IBRA Subregions (`r unique(thisTaxaData$geo2) %>% vec_to_sentence`). Figure \@ref(fig:map{{thisTaxa}}) shows the distribution of records for `r taxa`.

Using ICUN Red List methods, implemented via the `aoo` and `eoo` functions in the `red` package `r cite_package("red")`, the area of occupancy ([aoo](https://www.biodiversitya-z.org/content/species-area-of-occupancy-aoo).)) of _`r taxa`_ within the area of interest (`r aoiName`) was `r thisTaxaRed$aoo` km^2^ and the extent of occurrence ([eoo](https://www.biodiversitya-z.org/content/species-extent-of-occurrence-eoo)) was `r thisTaxaRed$eoo` km^2^.

<br>

```{r map{{thisTaxa}}, fig.cap = paste0("Map of records of _",taxa,"_")}

  mapRecords <- thisTaxaData %>%
    st_as_sf(coords = c("LONGITUDE","LATITUDE")
             , crs = 4283
             ) %>%
    st_transform(crs = 3577)

  tm_shape(LSA
           , bbox = st_bbox(mapRecords %>%
                              st_buffer(50)
                            )
           ) +
    tm_polygons(col = "REGION"
                , palette = lsaPalette
                ) +
  tm_shape(mapRecords) +
    tm_dots(col = "year"
            , size = 0.5
            ) +
  tm_layout(legend.format=list(fun=function(x) formatC(x, digits=0, format="d"))
            , legend.outside = TRUE
            , legend.outside.position = "left"
            )

```

### Models

```{r taxaModelPrep{{thisTaxa}}, include=FALSE}

  taxaModel = NULL

  for (i in thisTaxaMods$modLoop) {
    
    thisMod <- i
    
    taxaModel = c(taxaModel, knit_expand('child/taxaModel.Rmd'))
    
  }

```

`r paste(knit(text = taxaModel), collapse = '\n')`

### Overall

```{r dataOverall{{thisTaxa}}}

  taxaDat <- taxaModsOverall %>%
    dplyr::mutate(thisTaxa = gsub(" ","",Taxa)) %>%
    dplyr::filter(thisTaxa == summariseTaxa)

```

`r taxaDat$overall[[1]]$yearDiffText`. (Figure \@ref(fig:overallYearEffectPlot{{thisTaxa}})).

<br>

```{r overallYearEffectPlot{{thisTaxa}}, fig.width = 7, fig.cap = paste0("Overall effect of year on _",taxa,"_")}
  
  taxaDat$overall[[1]]$yearDiffOverallPlot

```

```{r addToSummary{{thisTaxa}}}

  taxaSummary <- tibble(Taxa = taxaDat$Taxa
                        , Common = taxaDat$Common
                        , overall = taxaDat$overall[[1]]$yearDiffOverallRes$text
                        )

  taxaModsSummary <- taxaModsSummary %>%
    dplyr::bind_rows(taxaSummary)

```