```{r data{{thisTaxa}}}

  taxa <- "{{thisTaxa}}"

  common <- taxaModsFull$Common[taxaModsFull$Taxa == taxa]

  taxaDat <- taxaModsFull %>%
    dplyr::filter(Taxa == taxa)

```

## _`rtaxa `_: `r common`

### Reporting rate

```{r rrData}

  mod <- taxaDat$rr[[1]]$mod

```

The model specification was:

``r format(formula(mod))``

This required the estimation of `r sum(!grepl("^b",names(coef(mod))))` parameters based on `r nrow(mod$data)` data points.

Figure \@ref(fig:rrFig{{thisTaxa}}) shows results from the reporting rate model. Table \@ref(tab:rrTab{{thisTaxa}}) shows the effect of year on reporting rate of _`r taxa`_.

_`r taxa`_ was `r taxaDat$llYearEff[[1]]$text`.

<br>

```{r rrFig{{thisTaxa}}, fig.cap = paste0("Reporting rate for _",taxa,"_")}

  taxaDat$rr[[1]]$plot

```

<br>

```{r rrTab{{thisTaxa}}}

  taxaDat$rrYearEff[[1]] %>%
    kable(caption = paste0("Effect of year on _"
                           , taxa
                           , "_ reporting rate"
                           )
          )

```

### List length

```{r llData}

  mod <- taxaDat$ll[[1]]$mod

```

The model specification was:

``r format(formula(mod))``

This required the estimation of `r sum(!grepl("^b",names(coef(mod))))` parameters based on `r nrow(mod$data)` data points.

Figure \@ref(fig:llFig{{thisTaxa}}) shows results from the list length model. Table \@ref(tab:llTab{{thisTaxa}}) shows the effect of year on reporting rate of _`r taxa`_.

_`r taxa`_ was `r taxaDat$llYearEff[[1]]$text`.

<br>

```{r llFig{{thisTaxa}}, fig.cap = paste0("Effet of year on list length corrected reporting rate for _",taxa,"_ at three different list lengths")}

  taxaDat$ll[[1]]$plot

```

<br>

```{r llTab{{thisTaxa}}}

  taxaDat$llYearEff[[1]] %>%
    kable(caption = paste0("Effect of year on list length corrected reporting rate for _"
                           , taxa
                           , "_"
                           )
          )

```
