```{r data{{thisTaxa}}}

  summariseTaxa <- "{{thisTaxa}}"

  taxaDat <- taxaModsFull %>%
    dplyr::mutate(thisTaxa = gsub(" ","",Taxa)) %>%
    dplyr::filter(thisTaxa == summariseTaxa)

  taxa <- taxaDat$Taxa[[1]]

  common <- taxaDat$Common[[1]]

```

## _`r taxa`_: `r common`

_`r taxa`_ is a member of the `r taxaDat %>% dplyr::pull(!!ensym(taxGroup))` `r tolower(taxGroup)`. Lists and list lengths were defined only for `r taxaDat %>% dplyr::pull(!!ensym(taxGroup))`.

### Reporting rate

```{r rrData{{thisTaxa}}}

  mod <- taxaDat$rr[[1]]$mod

```

The model specification was:

``r format(formula(mod))``

This required the estimation of `r sum(!grepl("^b",names(coef(mod))))` parameters based on `r nrow(mod$data)` data points.

Figure \@ref(fig:rrFig{{thisTaxa}}) shows results from the reporting rate model. Table \@ref(tab:rrTab{{thisTaxa}}) shows the effect of year on reporting rate of _`r taxa`_.

_`r taxa`_ was `r vec_to_sentence(taxaDat$rrYearEff[[1]]$text)`.

<br>

```{r rrFig{{thisTaxa}}, fig.height = 8, fig.width = 7, fig.cap = paste0("Reporting rate for _",taxa,"_")}

  taxaDat$rr[[1]]$plot

```

<br>

```{r rrTab{{thisTaxa}}}

  taxaDat$rrYearEff[[1]] %>%
    dplyr::select(`IBRA Subregion` = geo2
                  , `Probability of decline` = decreasing
                  , `Likelihood of decline` = likelihood
                  ) %>%
    kable(caption = paste0("Effect of year on _"
                           , taxa
                           , "_ reporting rate"
                           )
          )

```

<br>

### List length

```{r llData{{thisTaxa}}}

  mod <- taxaDat$ll[[1]]$mod

```

The model specification was:

``r format(formula(mod))``

This required the estimation of `r sum(!grepl("^b",names(coef(mod))))` parameters based on `r nrow(mod$data)` data points.

Figure \@ref(fig:llFig{{thisTaxa}}) shows results from the list length model. Table \@ref(tab:llTab{{thisTaxa}}) shows the effect of year on reporting rate of _`r taxa`_.

_`r taxa`_ was `r vec_to_sentence(taxaDat$llYearEff[[1]]$text)`.

<br>

```{r llFig{{thisTaxa}}, fig.height = 8, fig.width = 7, fig.cap = paste0("Effect of year on list length corrected reporting rate for _",taxa,"_ at three different list lengths (quantiles of ",vec_to_sentence(quantProbs),")")}

  taxaDat$ll[[1]]$plot

```

<br>

```{r llTab{{thisTaxa}}}

  taxaDat$llYearEff[[1]] %>%
    dplyr::select(`IBRA Subregion` = geo2
                  , `Probability of decline` = decreasing
                  , `Likelihood of decline` = likelihood
                  ) %>%
    kable(caption = paste0("Effect of year on list-length-corrected reporting-rate for _"
                           , taxa
                           , "_ at median list length of "
                           , median(taxaDat$ll[[1]]$mod$data$listLength)
                           )
          )

```

<br>

### Overall

Treating each method and each geographic area as equivalent in determining overall trend, _`r taxa`_ was `r taxaDat$overall`.
