```{r data{{thisTaxa}}}

  summariseTaxa <- "{{thisTaxa}}"

  taxaDat <- taxaModsOverall %>%
    dplyr::mutate(thisTaxa = gsub(" ","",Taxa)) %>%
    dplyr::filter(thisTaxa == summariseTaxa)

  taxa <- taxaDat$Taxa[[1]]

  common <- taxaDat$Common[[1]]
  
```

## _`r taxa`_: `r common`

### Reporting rate

```{r rrData{{thisTaxa}}}

  mod <- taxaDat$modRR[[1]]

  modType <- "reporting rate"

```

The model specification was:

``r format(formula(mod))``

This required the estimation of `r sum(!grepl("^b",names(as_tibble(mod))))` parameters based on `r nrow(mod$data)` data points.

Figure \@ref(fig:rrFig{{thisTaxa}}) shows results from the reporting rate model. Table \@ref(tab:rrTab{{thisTaxa}}) shows the effect of year on reporting rate of _`r taxa`_.

For _`r taxa`_, `r paste0("in ",recent, " compared with ", reference)`, `r modType` was `r vec_to_sentence(taxaDat$resRR[[1]]$yearDifferenceRes$text)` (Figure \@ref(fig:rrYearDiffPlot{{thisTaxa}})).

<br>

```{r rrFig{{thisTaxa}}, fig.height = 8, fig.width = 7, fig.cap = paste0("Reporting rate for _",taxa,"_")}

  taxaDat$resRR[[1]]$plotRibbon

```

<br>

```{r rrTab{{thisTaxa}}}

  taxaDat$resRR[[1]]$yearDifferenceRes %>%
    dplyr::select(`IBRA Region` = geo1
                  , `IBRA Subregion` = geo2
                  , `Probability` = lower
                  , `Likelihood` = likelihood
                  ) %>%
    kable(caption = paste0("Likelihood of "
                                 ,recent
                                 ," reporting rate being lower than "
                                 ,reference
                                 )
          )

```

<br>

```{r rrYearDiffPlot{{thisTaxa}}, fig.height = 8, fig.width = 7, fig.cap = paste0("Difference in ",testYears$year[testYears$type == "recent"]," ",tolower(modType)," compared to ",testYears$year[testYears$type == "reference"]," for _",taxa,"_")}

  taxaDat$resRR[[1]]$yearDifferencePlot

```

<br>

### List length

```{r llData{{thisTaxa}}}

  mod <- taxaDat$modLL[[1]]

  modType <- "list length corrected reporting rate"

```

The model specification was:

``r format(formula(mod))``

This required the estimation of `r sum(!grepl("^b",names(as_tibble(mod))))` parameters based on `r nrow(mod$data)` data points.

Figure \@ref(fig:llFig{{thisTaxa}}) shows results from the list length model. Table \@ref(tab:llTab{{thisTaxa}}) shows the effect of year on reporting rate of _`r taxa`_.

For _`r taxa`_, `r paste0("in ",recent, " compared with ", reference)`, `r modType` was `r vec_to_sentence(taxaDat$resLL[[1]]$yearDifferenceRes$text)` (Figure \@ref(fig:llYearDiffPlot{{thisTaxa}})).

<br>

```{r llFig{{thisTaxa}}, fig.height = 8, fig.width = 7, fig.cap = paste0("List length corrected reporting rate for _",taxa,"_")}

  taxaDat$resLL[[1]]$plotRibbon

```

<br>

```{r llTab{{thisTaxa}}}

  medianLL <- unique(taxaDat$resLL[[1]]$yearDifferenceRes$listLength)

  taxaDat$resLL[[1]]$yearDifferenceRes %>%
    dplyr::select(`IBRA Region` = geo1
                  , `IBRA Subregion` = geo2
                  , `Probability` = lower
                  , `Likelihood` = likelihood
                  ) %>%
    kable(caption = paste0("Likelihood of "
                           ,recent
                           ," list length corrected reporting rate being lower than "
                           ,reference
                           , " at median list length of "
                           , medianLL
                           )
          )

```

<br>

```{r llYearDiffPlot{{thisTaxa}}, fig.height = 8, fig.width = 7, fig.cap = paste0("Effect of year on list-length-corrected reporting-rate for _", taxa, "_ at median list length of ", medianLL)}

  taxaDat$resLL[[1]]$yearDifferencePlot

```

<br>

### Overall

Treating each method and each geographic area as equivalent in determining overall trend, _`r taxa`_ was `r taxaDat$overall[[1]]$yearDiffOverallRes$text` (Figure \@ref(fig:overallYearEffectPlot{{thisTaxa}})).

<br>

```{r overallYearEffectPlot{{thisTaxa}}, fig.width = 7, fig.cap = paste0("Overall effect of year on _",taxa,"_")}

  taxaDat$overall[[1]]$yearDiffOverallPlot  

```
