```{r dataMod{{thisMod}}}

  useMod <- "{{thisMod}}"
  
  thisMod <- thisTaxaMods %>%
    dplyr::filter(modLoop == useMod) %>%
    dplyr::mutate(resPath = gsub("Mod","Res",modPath)
                  , res = map(resPath,read_rds)
                  )
  
  modType <- thisMod$type

```

#### `r modType`

```{r data{{thisMod}}}

  mod <- read_rds(thisMod$modPath[[1]])

```

The model specification was:

``r format(formula(mod))``

This required the estimation of `r sum(!grepl("^b",names(as_tibble(mod))))` parameters based on `r nrow(mod$data)` data points.

Figure \@ref(fig:modFig{{thisMod}}) shows results from the reporting rate model. Table \@ref(tab:modTab{{thisMod}}) shows the effect of year on reporting rate of _`r taxa`_.

For _`r taxa`_, `r paste0("in ",recent, " compared with ", reference)`, `r modType` was `r vec_to_sentence(thisMod$res[[1]]$yearDifferenceRes$text)` (Figure \@ref(fig:modYearDiffPlot{{thisMod}})).

<br>

```{r modFig{{thisMod}}, fig.height = 8, fig.width = 7, fig.cap = paste0("Reporting rate for _",taxa,"_")}

  thisMod$res[[1]]$plotLine

```

<br>

```{r modTab{{thisMod}}}

  thisMod$res[[1]]$yearDifferenceRes %>%
    dplyr::left_join(luGeo %>%
                       dplyr::rename(geo1 = IBRA_REG_N
                                     , geo2 = IBRA_SUB_N
                                     )
                       ) %>%
    dplyr::arrange(geo1,geo2) %>%
    dplyr::select(`IBRA Region` = geo1
                  , `IBRA Subregion` = geo2
                  , `Probability` = lower
                  , `Likelihood` = likelihood
                  ) %>%
    kable(caption = paste0("Likelihood of "
                                 ,recent
                                 ," reporting rate being lower than "
                                 ,reference
                           )
          )

```

<br>

```{r modYearDiffPlot{{thisMod}}, fig.height = 8, fig.width = 7, fig.cap = paste0("Difference in ",testYears$year[testYears$type == "recent"]," ",tolower(modType)," compared to ",testYears$year[testYears$type == "reference"]," for _",taxa,"_")}

  thisMod$res[[1]]$yearDifferencePlot

```

<br>