```{r data{{thisTaxGroup}}}

  useTaxGroup <- "{{thisTaxGroup}}"

  taxGroupDat <- datTidy %>%
    dplyr::distinct(!!ensym(taxGroup),Taxa,Common) %>%
    dplyr::mutate(thisTaxGroup = gsub(" ","",!!ensym(taxGroup))) %>%
    dplyr::filter(thisTaxGroup == useTaxGroup)

  nTaxGroup <- datTidy %>%
    dplyr::filter(!!ensym(taxGroup) == useTaxGroup) %>%
    dplyr::count(Taxa,Common)
  
  commonInTaxGroup <- nTaxGroup %>%
    dplyr::top_n(5) %>%
    dplyr::mutate(text = case_when(is.na(Common) ~ Taxa
                                   , !is.na(Common) ~ paste0("_",Taxa,"_: ",Common)
                                   )
                  )

```

# `r useTaxGroup`

The [GBIF taxonomic backbone](https://www.gbif.org/dataset/d7dddbf4-2cf0-4f39-9b2a-bb099caae36c) lists `r useTaxGroup` as `r taxGroupNames %>% dplyr::filter(!!ensym(taxGroup) == useTaxGroup) %>% dplyr::pull(Common) %>% paste0(collapse = "|") %>% tolower()`.

The most common `r useTaxGroup` taxa in the data set included `r vec_to_sentence(commonInTaxGroup$text)`. In total there were `r nrow(nTaxGroup)` `r useTaxGroup` in the data set, setting an upper limit to the maximum possible list length - although this was adjusted down to the number of `r useTaxGroup` with records in each IBRA Subregion.

```{r taxGroupPrep{{thisTaxGroup}}, include=FALSE}

  taxaExp = NULL

  taxaLoop <- taxGroupDat %>%
    dplyr::inner_join(taxaModsOverall[,c("Taxa")]) %>%
    purrr::when(testRmd ~ (.) %>%
                  dplyr::sample_n(nrow(.)) %>%
                  dplyr::slice(1:3)
                , !testRmd ~ (.)
                ) %>%
    dplyr::pull(Taxa) %>%
    sort() %>%
    gsub(" ","",.)
    

  for (i in taxaLoop) {
    
    thisTaxa <- i
    
    taxaExp = c(taxaExp, knit_expand('child/taxaSummary.Rmd'))
    
  }

```

`r paste(knit(text = taxaExp), collapse = '\n')`